\pkg{shorts}: An R Package for Modeling Short Sprints

### 2020-10-21 paper.Rmd
Mladen changes

gg <- ggplot(
  kinematics_long,
  aes(x = time, y = value, color = Athlete)
) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  facet_wrap(
    ~variable,
    scales = "free_y",
    labeller = label_parsed
  ) +
  ylab(NULL) +
  xlab("Time (s)") +
  theme(legend.position = "top", legend.title = element_blank())

@@

```{r four-athletes-profile, echo=FALSE, fig.cap="Acceleration-Velocity profile of four athletes with different MSS and MAC parameters."}
gg <- ggplot(
  kinematics,
  aes(x = velocity, y = acceleration, color = Athlete)
) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  ylab(expression("Acceleration (ms"^-2 * ")")) +
  xlab(expression("Velocity (ms"^-1 * ")")) +
  theme(legend.position = "top", legend.title = element_blank())

@@

Here is a plot of observed and model predicted split times, with the help of the \pkg{ggplot2} package [@R-ggplot2]:

```{r}
require(ggplot2)

df <- data.frame(
  distance = split_distance,
  time = split_time,
  pred_time = predict_time_at_distance(
    distance = split_distance,
    MSS = m1$parameters$MSS,
    TAU = m1$parameters$TAU
  )
)

ggplot(df, aes(x = distance)) +
  theme_bw(8) +
  geom_line(aes(y = time)) +
  geom_point(aes(y = pred_time), color = "red") +
  xlab("Distance (m)") +
  ylab("Time (s)")
```

@@

Plotting the model predictions can be done once we convert data from wide to long with the help of \pkg{dplyr} [@R-dplyr], \pkg{tidyr} [@R-tidyr], and \pkg{tidyverse} [@R-tidyverse] packages:

@@

head(split_times)

@@

The following plot contains kinematics for all athletes in `split_times` dataset. Please note that power calculation takes default parameters for each individual:

@@

ggplot(
  filter(df, distance < 40),
  aes(x = distance, y = value, group = athlete, color = athlete)
) +
  theme_bw(8) +
  facet_wrap(~name, scales = "free_y") +
  geom_line(alpha = 0.7) +
  ylab(NULL) +
  xlab("Distance (m)") +
  theme(legend.position = "top", legend.title = element_blank())
```

@@

head(radar_gun_data)

@@

One source of error in the modeled estimation using a radar gun is the time synchronization. In theory, synchronization is ideal when a sprint is initiated at $t=0$ (i.e., $v(t=0) = 0$). In practice, this is often not the case. Let's use our athlete and add and deduct 0.5s to simulate an error in synchronization and its effect on estimated MSS and TAU.

```{r}
df <- tibble(
  `true time` = sprint_time,
  velocity = sprint_velocity,
  `0.5s added` = `true time` + 0.5,
  `0.5s deducted` = `true time` - 0.5
)

```{r}
plot_df <- pivot_longer(df, cols = -2, names_to = "Sync issue")

ggplot(plot_df, aes(x = value, y = velocity, color = `Sync issue`)) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  xlab("Time (s)") +
  ylab(expression("Velocity (" * ms^-1 * ")"))
```

@@

ggplot(plot_df, aes(x = distance, y = time, color = athlete, group = athlete)) +
  theme_bw(8) +
  geom_point() +
  geom_line() +
  xlab("Distance (m)") +
  ylab("Time (s)")
```

@@

# Add small noise to allow model fit
set.seed(1667)
rand_noise <- rnorm(nrow(sim_df), 0, 10^-4)
sim_df$time <- sim_df$time + rand_noise

head(sim_df)
```

@@

  cbind(data, params, data.frame(predicted_time = as.numeric(predicted_time)))
}

# estimated parameters and predited time
model_df <- sim_df %>%
  group_by(MSS, TAU, flying_start_distance) %>%
  do(pred_wrapper(.)) %>%
  ungroup()

@@

# MSS
ggplot(df, aes(x = flying_start_distance, y = est_MSS, color = MAC_string)) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  facet_wrap(~MSS_string, scales = "free_y") +
  xlab("Flying start distance (m)") +
  ylab("estimated MSS (m/s)") +
  theme(legend.title = element_blank())
```

@@

```{r}
# MAC
ggplot(df, aes(x = flying_start_distance, y = est_MAC, color = MSS_string)) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  facet_wrap(~MAC_string, scales = "free_y") +
  xlab("Flying start distance (m)") +
  ylab("estimated MAC (m/s/s)") +
  theme(legend.title = element_blank())
```

@@

```{r}
# PMAX
ggplot(df, aes(x = flying_start_distance, y = est_PMAX, color = MSS_string)) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  facet_wrap(~MAC_string, scales = "free_y") +
  xlab("Flying start distance (m)") +
  ylab("estimated PMAX (W/kg)") +
  theme(legend.title = element_blank())
```

@@

ggplot(model_df, aes(y = residuals, x = distance, color = flying_start_distance, group = group)) +
  theme_bw(8) +
  geom_line(alpha = 0.3) +
  facet_grid(MSS_string ~ MAC_string) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_color_gradientn(colours = terrain.colors(5, rev = FALSE)) +
  xlab("Distance (m)") +
  ylab("Predicted time - observed time (s)")
```

@@

```{r}
ggplot(model_df, aes(y = residuals, x = distance, color = flying_start_distance, group = group)) +
  theme_bw(8) +
  geom_line(alpha = 0.3) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_color_gradientn(colours = terrain.colors(5, rev = FALSE)) +
  xlab("Distance (m)") +
  ylab("Predicted time - observed time (s)")
```

@@

# estimated parameters and predited time
model_df <- sim_df %>%
  group_by(MSS, TAU, flying_start_distance) %>%
  do(pred_wrapper(.)) %>%
  ungroup()
```

@@

# MSS
ggplot(df, aes(x = flying_start_distance, y = est_MSS, color = model)) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  facet_grid(MSS_string ~ MAC_string, scales = "free_y") +
  xlab("Flying start distance (m)") +
  ylab("estimated MSS (m/s)") +
  theme(legend.title = element_blank())
```

@@

```{r}
# MAC
ggplot(df, aes(x = flying_start_distance, y = est_MAC, color = model)) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  facet_grid(MAC_string ~ MSS_string, scales = "free_y") +
  xlab("Flying start distance (m)") +
  ylab("estimated MAC (m/s/s)") +
  theme(legend.title = element_blank())
```

@@

```{r}
# PMAX
ggplot(df, aes(x = flying_start_distance, y = est_PMAX, color = model)) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  facet_grid(MAC_string ~ MSS_string, scales = "free_y") +
  xlab("Flying start distance (m)") +
  ylab("estimated PMAX (W/kg)") +
  theme(legend.title = element_blank())
```

@@

```{r}
# time_correction
ggplot(df, aes(x = flying_start_distance, y = est_time_correction, color = model)) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  geom_line(aes(y = stolen_time), color = "black", linetype = "dashed") +
  facet_grid(MAC_string ~ MSS_string, scales = "free_y") +
  xlab("Flying start distance (m)") +
  ylab("estimated time correction (s)") +
  theme(legend.title = element_blank())
```

@@

```{r}
# distance_correction
ggplot(df, aes(x = flying_start_distance, y = est_distance_correction, color = model)) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  geom_abline(slope = 1, color = "black", linetype = "dashed") +
  facet_grid(MAC_string ~ MSS_string, scales = "free_y") +
  xlab("Flying start distance (m)") +
  ylab("estimated distance correction (m)") +
  theme(legend.title = element_blank())
```

@@

ggplot(model_df, aes(y = residuals, x = distance, color = flying_start_distance, group = group)) +
  theme_bw(8) +
  geom_line(alpha = 0.3) +
  facet_wrap(~model) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_color_gradientn(colours = terrain.colors(5, rev = FALSE)) +
  xlab("Distance (m)") +
  ylab("Predicted time - observed time (s)")
```

@@

# MSS
ggplot(df, aes(x = time_lag, y = est_MSS, color = model)) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  facet_grid(MSS_string ~ MAC_string, scales = "free_y") +
  xlab("Time lag (s)") +
  ylab("estimated MSS (m/s)") +
  theme(legend.title = element_blank())
```

@@

```{r}
# MAC
ggplot(df, aes(x = time_lag, y = est_MAC, color = model)) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  facet_grid(MAC_string ~ MSS_string, scales = "free_y") +
  xlab("Time lag (s)") +
  ylab("estimated MAC (m/s/s)") +
  theme(legend.title = element_blank())
```

@@

```{r}
# time_correction
ggplot(df, aes(x = time_lag, y = est_time_correction, color = model)) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  geom_abline(slope = -1, color = "black", linetype = "dashed") +
  facet_grid(MAC_string ~ MSS_string, scales = "free_y") +
  xlab("Time lag (s)") +
  ylab("estimated time correction (s)") +
  theme(legend.title = element_blank())
```

@@

```{r}
# distance_correction
ggplot(df, aes(x = time_lag, y = est_distance_correction, color = model)) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  facet_grid(MAC_string ~ MSS_string, scales = "free_y") +
  xlab("Time lag (s)") +
  ylab("estimated distance correction (m)") +
  theme(legend.title = element_blank())
```

@@

ggplot(model_df, aes(y = residuals, x = distance, color = time_lag, group = group)) +
  theme_bw(8) +
  geom_line(alpha = 0.3) +
  facet_wrap(~model) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_color_gradientn(colours = terrain.colors(5, rev = FALSE)) +
  xlab("Distance (m)") +
  ylab("Predicted time - observed time (s)")
```

@@

ggplot(df, aes(x = distance, y = resid, color = name)) +
  theme_bw(8) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point() +
  theme(legend.title = element_blank()) +
  xlab("Distance (m)") +
  ylab("Predicted - observed time (s)")
```

@@

# Convert data to long
df <- vescovi %>%
  select(1:13) %>%
  # slice(1:10) %>%
  pivot_longer(cols = 9:13, names_to = "distance", values_to = "time") %>%
  mutate(
    distance = as.numeric(str_extract(distance, "^[0-9]+"))
  )

@@

# Plot
ggplot(model_resid, aes(y = model)) +
  theme_bw(8) +
  geom_vline(
    data = model_SESOI,
    aes(xintercept = SESOI_lower), color = "blue", alpha = 0.5, linetype = "dashed"
  ) +
  geom_vline(
    data = model_SESOI,
    aes(xintercept = SESOI_upper), color = "blue", alpha = 0.5, linetype = "dashed"
  ) +
  geom_vline(xintercept = 0, color = "blue", alpha = 0.5) +
  geom_jitter(aes(x = resid), alpha = 0.1, height = 0.25) +
  geom_errorbarh(data = model_SESOI, aes(xmin = lower, xmax = upper), height = 0.1, color = "black") +
  geom_point(data = model_SESOI, aes(x = bias), color = "black") +
  facet_wrap(~distance, scales = "free_x") +
  xlab("Predicted time - observed time (s)") +
  ylab(NULL)
```

>>>>

gg <- ggplot(
  kinematics_long,
  aes(x = time, y = value, color = Athlete)
) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  facet_wrap(
    ~variable,
    scales = "free_y",
    labeller = label_parsed
  ) +
  ylab(NULL) +
  xlab("Time (s)") +
  theme(
    legend.position = "top",
    legend.title = element_blank())

@@

```{r four-athletes-profile, echo=FALSE, fig.cap="Acceleration-Velocity profile of four athletes with different MSS and MAC parameters."}
gg <- ggplot(
  kinematics,
  aes(x = velocity, y = acceleration, color = Athlete)
) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  ylab(expression("Acceleration (ms"^-2 * ")")) +
  xlab(expression("Velocity (ms"^-1 * ")")) +
  theme(
    legend.position = "top",
    legend.title = element_blank())

@@

@@

Plotting the model predictions can be done once we convert data from wide to long with the help of   \pkg{ggplot2} [@R-ggplot2], \pkg{dplyr} [@R-dplyr], \pkg{tidyr} [@R-tidyr], and \pkg{tidyverse} [@R-tidyverse] packages:

@@

@@

The following figure contains kinematics for all athletes in `split_times` dataset. Please note that power calculation takes default parameters for each individual:

@@

ggplot(
  filter(df, distance < 40),
  aes(x = distance, y = value, group = athlete, color = athlete)
) +
  theme_bw(8) +
  facet_wrap(~name, scales = "free_y") +
  geom_line(alpha = 0.7) +
  ylab(NULL) +
  xlab("Distance (m)") +
  theme(
    legend.position = "top",
    legend.title = element_blank())
```

@@

@@

One source of error in the modeled estimation using a radar gun is the time synchronization. In theory, synchronization is ideal when a sprint is initiated at $t=0$ (i.e., $v(t=0) = 0$). In practice, this is often not the case. Let's use our athlete and add and deduct 0.5s to simulate an error in synchronization and its effect on estimated MSS and TAU (Figure \@ref(fig:radar-gun-sync)).

```{r radar-gun-sync, include=FALSE, fig.cap="Radar gun synchronization issues"}
df <- tibble(
  `true time` = sprint_time,
  velocity = sprint_velocity,
  `0.5s added` = `true time` + 0.5,
  `0.5s deducted` = `true time` - 0.5
)

plot_df <- pivot_longer(df, cols = -2, names_to = "Sync issue")

ggplot(
  plot_df,
  aes(x = value, y = velocity, color = `Sync issue`)
) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  xlab("Time (s)") +
  ylab(expression("Velocity (" * ms^-1 * ")")) +
  theme(
    legend.title = element_blank(), 
    legend.position = "top")
```

@@

ggplot(
  plot_df,
  aes(x = distance, y = time, color = athlete, group = athlete)
) +
  theme_bw(8) +
  geom_point() +
  geom_line() +
  xlab("Distance (m)") +
  ylab("Time (s)") +
  theme(
    legend.title = element_blank(), 
    legend.position = "top")
```

@@

# Add small noise to allow model fit
set.seed(1667)
rand_noise <- rnorm(nrow(sim_df), 0, 10^-4)
sim_df$time <- sim_df$time + rand_noise
```

@@

  cbind(
    data,
    params,
    data.frame(predicted_time = as.numeric(predicted_time))
  )
}

# estimated parameters and predicted time
model_df <- sim_df %>%
  group_by(MSS, TAU, flying_start_distance) %>%
  do(pred_wrapper(.)) %>%
  ungroup()

@@

# MSS
ggplot(
  df,
  aes(x = flying_start_distance, y = est_MSS, color = MAC_string)
) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  facet_wrap(~MSS_string, scales = "free_y") +
  xlab("Flying start distance (m)") +
  ylab("estimated MSS (m/s)") +
  theme(
    legend.title = element_blank(), 
    legend.position = "top")
```

@@

```{r}
# MAC
ggplot(
  df,
  aes(x = flying_start_distance, y = est_MAC, color = MSS_string)
) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  facet_wrap(~MAC_string, scales = "free_y") +
  xlab("Flying start distance (m)") +
  ylab("estimated MAC (m/s/s)") +
  theme(
    legend.title = element_blank(), 
    legend.position = "top")
```

@@

```{r}
# PMAX
ggplot(
  df,
  aes(x = flying_start_distance, y = est_PMAX, color = MSS_string)
) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  facet_wrap(~MAC_string, scales = "free_y") +
  xlab("Flying start distance (m)") +
  ylab("estimated PMAX (W/kg)") +
  theme(
    legend.title = element_blank(), 
    legend.position = "top")
```

@@

ggplot(
  model_df,
  aes(y = residuals, x = distance, color = flying_start_distance, group = group)
) +
  theme_bw(8) +
  geom_line(alpha = 0.3) +
  facet_grid(MSS_string ~ MAC_string) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_color_gradientn(colours = terrain.colors(5, rev = FALSE)) +
  xlab("Distance (m)") +
  ylab("Predicted time - observed time (s)") +
  theme(legend.position = "top") + 
  labs(color = "Flying start distance")
```

@@

```{r}
ggplot(
  model_df,
  aes(y = residuals, x = distance, color = flying_start_distance, group = group)
) +
  theme_bw(8) +
  geom_line(alpha = 0.3) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_color_gradientn(colours = terrain.colors(5, rev = FALSE)) +
  xlab("Distance (m)") +
  ylab("Predicted time - observed time (s)") +
  theme(legend.position = "top") + 
  labs(color = "Flying start distance")
```

@@

# estimated parameters and predicted time
model_df <- sim_df %>%
  group_by(MSS, TAU, flying_start_distance) %>%
  do(pred_wrapper(.)) %>%
  ungroup()
```

@@

# MSS
ggplot(
  df,
  aes(x = flying_start_distance, y = est_MSS, color = model)
) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  facet_grid(MSS_string ~ MAC_string, scales = "free_y") +
  xlab("Flying start distance (m)") +
  ylab("estimated MSS (m/s)") +
  theme(
    legend.title = element_blank(),
    legend.position = "top")
```

@@

```{r}
# MAC
ggplot(
  df,
  aes(x = flying_start_distance, y = est_MAC, color = model)
) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  facet_grid(MAC_string ~ MSS_string, scales = "free_y") +
  xlab("Flying start distance (m)") +
  ylab("estimated MAC (m/s/s)") +
  theme(
    legend.title = element_blank(),
    legend.position = "top")
```

@@

```{r}
# PMAX
ggplot(
  df,
  aes(x = flying_start_distance, y = est_PMAX, color = model)
) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  facet_grid(MAC_string ~ MSS_string, scales = "free_y") +
  xlab("Flying start distance (m)") +
  ylab("estimated PMAX (W/kg)") +
  theme(
    legend.title = element_blank(),
    legend.position = "top")
```

@@

```{r}
# time_correction
ggplot(
  df,
  aes(x = flying_start_distance, y = est_time_correction, color = model)
) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  geom_line(aes(y = stolen_time), color = "black", linetype = "dashed") +
  facet_grid(MAC_string ~ MSS_string, scales = "free_y") +
  xlab("Flying start distance (m)") +
  ylab("estimated time correction (s)")  +
  theme(
    legend.title = element_blank(),
    legend.position = "top")
```

@@

```{r}
# distance_correction
ggplot(
  df,
  aes(x = flying_start_distance, y = est_distance_correction, color = model)
) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  geom_abline(slope = 1, color = "black", linetype = "dashed") +
  facet_grid(MAC_string ~ MSS_string, scales = "free_y") +
  xlab("Flying start distance (m)") +
  ylab("estimated distance correction (m)") +
  theme(
    legend.title = element_blank(),
    legend.position = "top")
```

@@

ggplot(
  model_df,
  aes(y = residuals, x = distance, color = flying_start_distance, group = group)
) +
  theme_bw(8) +
  geom_line(alpha = 0.3) +
  facet_wrap(~model) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_color_gradientn(colours = terrain.colors(5, rev = FALSE)) +
  xlab("Distance (m)") +
  ylab("Predicted time - observed time (s)") +
  theme(legend.position = "top") + 
  labs(color = "Flying start distance")
```

@@

# MSS
ggplot(df, aes(x = time_lag, y = est_MSS, color = model)) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  facet_grid(MSS_string ~ MAC_string, scales = "free_y") +
  xlab("Time lag (s)") +
  ylab("estimated MSS (m/s)") +
  theme(
    legend.title = element_blank(),
    legend.position = "top")
```

@@

```{r}
# MAC
ggplot(df, aes(x = time_lag, y = est_MAC, color = model)) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  facet_grid(MAC_string ~ MSS_string, scales = "free_y") +
  xlab("Time lag (s)") +
  ylab("estimated MAC (m/s/s)") +
  theme(
    legend.title = element_blank(),
    legend.position = "top")
```

@@

```{r}
# time_correction
ggplot(
  df,
  aes(x = time_lag, y = est_time_correction, color = model)
) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  geom_abline(slope = -1, color = "black", linetype = "dashed") +
  facet_grid(MAC_string ~ MSS_string, scales = "free_y") +
  xlab("Time lag (s)") +
  ylab("estimated time correction (s)") +
  theme(
    legend.title = element_blank(),
    legend.position = "top")
```

@@

```{r}
# distance_correction
ggplot(
  df,
  aes(x = time_lag, y = est_distance_correction, color = model)
) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  facet_grid(MAC_string ~ MSS_string, scales = "free_y") +
  xlab("Time lag (s)") +
  ylab("estimated distance correction (m)") +
  theme(
    legend.title = element_blank(),
    legend.position = "top")
```

@@

ggplot(
  model_df,
  aes(y = residuals, x = distance, color = time_lag, group = group)
) +
  theme_bw(8) +
  geom_line(alpha = 0.3) +
  facet_wrap(~model) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_color_gradientn(colours = terrain.colors(5, rev = FALSE)) +
  xlab("Distance (m)") +
  ylab("Predicted time - observed time (s)")  +
  theme(legend.position = "top") + 
  labs(color = "Time lag")
```

@@

ggplot(df, aes(x = distance, y = resid, color = name)) +
  theme_bw(8) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point() +
  theme(legend.title = element_blank()) +
  xlab("Distance (m)") +
  ylab("Predicted - observed time (s)") +
  theme(
    legend.title = element_blank(),
    legend.position = "top")
```

@@

# Convert data to long
df <- vescovi %>%
  select(1:13) %>%
  # slice(1:10) %>%
  pivot_longer(
    cols = 9:13,
    names_to = "distance",
    values_to = "time"
  ) %>%
  mutate(
    distance = as.numeric(str_extract(distance, "^[0-9]+"))
  )
```

@@

# Plot
ggplot(model_resid, aes(y = model)) +
  theme_bw(8) +
  geom_vline(
    data = model_SESOI,
    aes(xintercept = SESOI_lower),
    color = "blue", alpha = 0.5, linetype = "dashed"
  ) +
  geom_vline(
    data = model_SESOI,
    aes(xintercept = SESOI_upper),
    color = "blue", alpha = 0.5, linetype = "dashed"
  ) +
  geom_vline(xintercept = 0, color = "blue", alpha = 0.5) +
  geom_jitter(aes(x = resid), alpha = 0.1, height = 0.25) +
  geom_errorbarh(
    data = model_SESOI,
    aes(xmin = lower, xmax = upper),
    height = 0.1, color = "black"
  ) +
  geom_point(data = model_SESOI, aes(x = bias), color = "black") +
  facet_wrap(~distance, scales = "free_x") +
  xlab("Predicted time - observed time (s)") +
  ylab(NULL)
```
